\begin{frame}[fragile]{Bug fixes}
\begin{itemize}
\item Missing memory fence in \texttt{RandomPool::free\_state} functions.
      Possible race condition sometimes led to repeated random number
      sequences on different threads with CUDA.
\item Fix wrong behavior for corner case in
      \texttt{Kokkos::Experimental::is\_partitioned} algorithm.
\item Wrong implementation for \texttt{cyl\_bessel\_i0} yielding unexpected
      NaNs. Special mathematical functions still belong to
      \texttt{Kokkos::Experimental::}.
\item Bug in OpenMPTarget with init/join in reducers.
\item Resolve symlink creation issue at configuration time on Windows.
\item Minor fixes to \texttt{Kokkos::Array} (mostly anecdotal).
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Bug fixes}
\begin{itemize}
\item Fix corner cases when deep copying empty views that can lead to
      undefined behavior.
\item Uninitialized variable in \texttt{parallel\_for(TeamPolicy)} affecting
      level 1 scratch pad memory in the CUDA backend (introduced in 4.1).
\item Fix bug in CUDA PTX for atomic min/max operations of 64-bit integers.
      Wrong answer when mixing negative and positive values.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Bug fixes}
Fixes to be included in 4.2.01
\begin{itemize}
\item Accidental finalization of tools when non-default host execution space
      instance is deleted.
\item Missing \texttt{inline} in new HIP graph implementation leading to
      multiple definition linking error downstream.
\item Add warp synchronization in CUDA \texttt{parallel\_reduce} to avoid
      possible race conditions reported by \texttt{cuda-memcheck}.
\item Workaround bogus deprecated declarations warning for GCC versions less than 11
\item Fix MSVC CUDA build (missing header include)
\end{itemize}
\end{frame}

