%==========================================================================

\begin{frame}[fragile]

  {\Huge Backend Updates}

  \vspace{10pt}

\end{frame}

%==========================================================================

\begin{frame}[fragile]

  {\Huge CUDA}

  \vspace{10pt}

\end{frame}

\begin{frame}[fragile]{Features and Fixes for \texttt{CUDA}}

  \begin{itemize}
    \item Added support for \texttt{Kokkos\_ARCH\_BLACKWELL103} for B300 GPUs (requires \texttt{CUDA} $\geq 12.8$).
    \item Fixed building with \texttt{clang} when enabling both \texttt{CUDA} and \texttt{OpenMP}.
    \item Added support for the flags \texttt{-Ofc} and \texttt{--fdevice-time-trace} to \texttt{nvcc\_wrapper} (Useful for getting insights into compile time).
  \end{itemize}

\end{frame}

\begin{frame}[fragile]{SIMD support on ARM with NVCC}
  \texttt{nvcc} $>$ 12.8 allows to use \texttt{NEON} instructions.
  \begin{itemize}
    \item With \texttt{Kokkos\_ARCH\_NATIVE=ON} we run checks if the compiler supports \texttt{NEON} and \texttt{SVE}. If the compiler supports them we enable them.
    \item For all manually specified ARM architectures we enable them if the architecture supports them by specification. We do \textbf{not} check if the compiler supports them.
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]

  {\Huge HIP}

  \vspace{10pt}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Features and Fixes for \texttt{HIP}}

  \begin{itemize}
    \item Added support for \texttt{Kokkos\_ARCH\_AMD\_GFX950} for MI350 and MI355 (requires \texttt{ROCm} $\geq 7.0$ recommended $\geq 7.1$)
    \item Added support for \texttt{bhalf\_t} (in \texttt{Kokkos::Experimental}).
    \item Added math functions for \texttt{half\_t} and \texttt{bhalf\_t} instead of casting to \texttt{float}.
	\item Workaround race condition reported in \texttt{parallel\_scan} when running on MI300A
  	\begin{itemize}
		\item Added an extra synchronization at the end of \texttt{parallel\_scan} implementation.
		\item Seems to be a compiler bug on MI300A.
		\item Extra overhead is negligible.
  	\end{itemize}
    \item Implemented support for \texttt{StaticBatchSize} policy trait
  \end{itemize}

\end{frame}

\begin{frame}[fragile]{\texttt{HIP} \texttt{parallel\_scan} Performance}
  \begin{figure}[ht]
    \centering
    \begin{tikzpicture}
      \begin{axis}[
        width=0.99\textwidth,
        height=0.35\textwidth,
        grid=major,
        ymin=0,
        ybar,
        ybar=5pt,
        bar width=6pt,
        enlargelimits=0.15,
        legend style={at={(0.5, 1.3)},
          anchor=north,legend columns=-1,font=\small},
		  xlabel={Input Array Size},
		  ylabel={Execution Time (sec)},
        symbolic x coords={64, 128, 256, 512, 1024, 2048, 4096, 8192, 16384, 32768, 65536},
        xtick=data,
        x tick label style={at={(0.0, -0.5)},font=\small},
        ]
		  \addplot[color=red!60, fill=red!40] coordinates {(64, 2.05E-05) (128, 2.07E-05) (256, 2.01E-05) (512, 2.11E-05) (1024,  2.18E-05) (2048, 2.20E-05) (4096, 2.16E-05) (8192, 2.37E-05) (16384, 2.58E-05) (32768, 3.20E-05) (65536, 4.36E-05)};
		  \addplot[color=green!60, fill=green!40] coordinates {(64, 2.15E-05) (128, 2.10E-05) (256, 2.02E-05) (512, 2.16E-05) (1024, 2.20E-05) (2048, 2.15E-05) (4096, 2.31E-05) (8192, 2.34E-05) (16384, 2.61E-05) (32768, 3.15E-05) (65536, 4.37E-05)};
      \legend{Old ParalleScan, New ParallelScan}
      \end{axis}
    \end{tikzpicture}
  \end{figure}
  \begin{itemize}
	  \item \texttt{parallel\_scan} Performance on MI300A
  \end{itemize}
\end{frame}
