%==========================================================================

\begin{frame}[fragile]

  {\Huge General Enhancements}

  \vspace{10pt}

\end{frame}

\begin{frame}[fragile]{General Enhancements I}
  \begin{itemize}
    \item Enable ScatterView contribute into a View that is a rvalue
    \item Use \texttt{Array::size\_type} for subscript operators
    \item Use StaticBatchSize in ViewFill
    \item Improve performance of \texttt{deep\_copy} from scalar in view fill using \texttt{StaticBatchSize}
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{General Enhancements II}
  \begin{itemize}
    \item Enforce failure when exceeding \texttt{team\_size\_max} and \texttt{scratch\_size\_max} checks
    \item Enable MPI detection with PALS
    \item Add \texttt{Kokkos::norm} for \texttt{Kokkos::complex} similar to \texttt{std::norm}
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{SIMD Enhancements}
  \begin{itemize}
    \item Add bitwise operators to simd vectors of integral types and simd masks
    \item Add simd memory permute functions
    \item Use neon and sve SIMD instructions if nvcc supports them
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{MDRangePolicy overhaul}
  Improved performance for \texttt{MDRangePolicy} for all rank (2 to 6) for \texttt{CUDA}, \texttt{HIP} and \texttt{SYCL}
  \begin{itemize}
    \item Rewrite internal logic for computing functor indices
    \item Fix performance discrepancies between iterate Left and Right
  \end{itemize}

  \vspace{5pt}
  Note: Doesn't concern nested multidimensional policy like \texttt{TeamThreadMDRange} or \texttt{TeamVectorMDRange}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{MDRangePolicy overhaul}
  Change the default tile size for \texttt{CUDA}, \texttt{HIP}, and \texttt{SYCL} backends.
  Use more threads for the dimension that accesses memory in a coalesced way.
  \vspace{10pt}
  \begin{itemize}
    \item Lower register usage for the same kernel
    \item Better memory throughput for memory-intensive kernels.
    \item Better GPU occupancy for simple kernels.
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{MDRangePolicy overhaul}
  \begin{figure}[ht]
    \centering
    \begin{tikzpicture}
      \begin{axis}[
        width=0.8\textwidth,
        height=0.35\textwidth,
        grid=major,
        ymin=0,
        ybar,
        ybar=5pt,
        bar width=12pt,
        enlargelimits=0.15,
        legend style={at={(0.5, 1.3)},
          anchor=north,legend columns=-1,font=\small},
        ylabel={Speedup},
        symbolic x coords={2D, 3D, 4D, 5D, 6D},
        xtick=data,
        x tick label style={at={(0.0, -0.5)},font=\small},
        ]
      \addplot[color=red!60, fill=red!40] coordinates {(2D, 1.23) (3D, 1.38) (4D, 1.56) (5D, 1.36) (6D, 2.16)};
      \addplot[color=green!60, fill=green!40] coordinates {(2D, 1.32) (3D, 1.00) (4D, 1.08) (5D, 1.42) (6D, 2.13)};
      \legend{AMD MI250X, Nvidia A100}
      \end{axis}
    \end{tikzpicture}
  \end{figure}
  \begin{itemize}
    \item Stream Add kernel ($C = A + B$) for different dimensions.
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{MDRangePolicy overhaul}
  \begin{figure}[ht]
    \centering
    \begin{tikzpicture}
      \begin{axis}[
        width=0.8\textwidth,
        height=0.35\textwidth,
        grid=major,
        ymin=0,
        ybar,
        ybar=10pt,
        bar width=15pt,
        enlargelimits=0.15,
        legend style={at={(0.5, 1.3)},
          anchor=north,legend columns=-1,font=\small},
        ylabel={Speedup},
        symbolic x coords={2D Left, 2D Right, 3D Left, 3D Right},
        xtick=data,
        x tick label style={at={(0.0, -0.5)},font=\small},
        ]
      \addplot[color=red!60, fill=red!40] coordinates {(2D Left, 1.44) (2D Right, 3.17) (3D Left, 1.00) (3D Right, 2.32)};
      \addplot[color=green!60, fill=green!40] coordinates {(2D Left, 1.94) (2D Right, 1.94) (3D Left, 1.01) (3D Right, 2.71)};
      \legend{AMD MI250X, Nvidia A100}
      \end{axis}
    \end{tikzpicture}
  \end{figure}
  \begin{itemize}
    \item Stencil kernel with 7 points and 9 points in 2D and 3D respectively.
  \end{itemize}
\end{frame}

%==========================================================================

\begin{frame}[fragile]{Expand math support}
  Increase \texttt{\textbf{half}} and \texttt{\textbf{bhalf}} support
  \begin{itemize}
    \item Add \texttt{denorm\_min} traits
    \item Add non standard \texttt{rcp}, \texttt{rcpf} and \texttt{rcpl} functions.
    \item Extend \texttt{rsqrt} to half types
  \end{itemize}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Expand math support}
  Implement all remaining math functions
  \begin{itemize}
    \item Add \texttt{modf}, \texttt{modff} and \texttt{modfl} functions
    \item Add mathematical functions \texttt{frexp} \texttt{ldexp}, \texttt{scalbn}, \texttt{scalbln}
    \item Provide more quadruple precision floating-point manipulation functions.
    \item Add \texttt{isnormal} function for all floating-point types.
    \item Add binary predicate math comparison functions.
    \item Add fpclassify function.
    \item Round to integer math functions \texttt{rint} and \texttt{round}.
    \item Add std \texttt{nexttoward} wrapper.
  \end{itemize}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{SIMD support on ARM}
  \texttt{nvcc} > 12.8 allows to use \texttt{NEON} instructions.
  \begin{itemize}
    \item With `KOKKOS\_ARCH\_NATIVE=ON` we run checks if the compiler supports \texttt{NEON} and \texttt{SVE}. If the compiler supports them we enable them.
    \item For all manually specified ARM architectures we enable them if the architecture supports them. We do \textbf{not} check if the compiler supports them.
  \end{itemize}
\end{frame}

