\begin{frame}{Kokkos Tools Quick Start}
\textbf{Learning Objectives:} 

\begin{itemize}
\item Quickly start using a tool via Kokkos Tools build system for any Kokkos application and backend.
\item Set environment variables of Kokkos Tools to customize its tools' behaviors.
\end{itemize}
\end{frame}


\begin{frame}{All the info so far is great...}
\begin{center}
I want to start using Kokkos Tools this minute for my use case. 
% <Optional text:>
% What's the tl;dr? 
\end{center}
\end{frame}

\begin{frame}[fragile]{Quick Start: Generic}
\begin{enumerate}
\small 
\item \textbf{Assume} an install prefix of your Kokkos build in \texttt{\$\{YOUR\_KOKKOS\}}.
\item \textbf{Obtain} via \texttt{git clone github.com/kokkos/kokkos-tools; cd kokkos-tools;} and load needed external software dependences.
\item \textbf{Install} with CMake:
\begin{lstlisting}
mkdir build; cd build; cmake ..
-DKokkos_ROOT="${YOUR_KOKKOS}"
-DCMAKE_INSTALL_PREFIX="${YOUR_KTO_INSTALL}";
make -j 4; make install;
\end{lstlisting}

\item \textbf{Set up} environment variables:
\begin{lstlisting}
export KOKKOS_TOOLS_GLOBAL<toolvar>=...
\end{lstlisting}
\item \textbf{Load} tool library via
\begin{lstlisting}
export KOKKOS_TOOLS_LIBS=
"${YOUR_KTO_INSTALL}/lib64/libkp_toolName.so"
\end{lstlisting}

\item \textbf{Run}: \texttt{cd /path/to/your/app; ./yourKokkosApp.exe};
\end{enumerate}

\end{frame}

\begin{frame}[fragile]{Quick Start: \texttt{nvtx-connector} on Perlmutter}

\begin{enumerate}
\small 

\item \textbf{Assume} an install prefix of Kokkos with the CUDA backend enabled in \texttt{\${YOUR\_KOKKOS}}.\\
\item \textbf{Obtain}
\begin{lstlisting}
git clone https://github.com/kokkos/kokkos-tools;
cd kokkos-tools; module load PrgEnv-gnu;
\end{lstlisting}
\item \textbf{Install} with CMake:
\begin{lstlisting}
mkdir build; cd build; cmake ..
-DKokkos_ROOT="${YOUR_KOKKOS}"
-DCMAKE_INSTALL_PREFIX="/where/to/install/the/tools";
make -j 4; make install;
\end{lstlisting}

\item \textbf{Set up}: 
\begin{lstlisting} 
export KOKKOS\_TOOLS\_GLOBALFENCES=1;
\end{lstlisting}

\item \textbf{Load}:
\begin{lstlisting}
export KOKKOS_TOOLS_LIBS=
"/where/to/install/the/tools/lib64/libkp_nvtx_connector.so";
\end{lstlisting}

\item \textbf{Run}: \texttt{cd /path/to/your/app; ncu -o profile ./yourKokkosApp.exe;}
\end{enumerate}
\end{frame}


\begin{frame}[fragile]{Additional Notes}
	\begin{enumerate}
	   \item For the latest default version of Kokkos Tools, make sure you are on the develop branch of the github repository and do a git pull.
	   \item Use \texttt{ccmake ..} instead of \texttt{cmake ..} for Kokkos Tools to see the list of Kokkos Tools options available.
	\end{enumerate}
\end{frame}


\begin{frame}[fragile]{Summary of Quick Start Guide}
To quickly start using a tool in Kokkos Tools for your Kokkos application, you do the following via git and CMake:
\begin{enumerate}
\item \textbf{Assume} an appropriate build of Kokkos is available.
\item \textbf{Obtain} the latest version of Kokkos Tools.
\item \textbf{Install} Kokkos Tools on your machine.
\item \textbf{Set up} installed tool libraries through specifying values for environment variables.
\item \textbf{Load} the Kokkos Tools tool library or libraries you want to use.
\item \textbf{Run} your Kokkos application, as usual.
\end{enumerate}

\begin{center}
\small See \url{https://github.com/kokkos/kokkos-tools/blob/develop/README.md}
for the latest. 
\end{center}

\end{frame}


