\begin{frame}[fragile]{Unmanaged Views}

  {\Huge Unmanaged Views: Dealing with external memory}

  \vspace{20pt}

  \textbf{Learning objectives:}
  \begin{itemize}
    \item{Why do you need unmanaged views}
    \item{Introduce unmanaged Views - basic capabilities and syntax}
    \item{Suggested usage and practices}
  \end{itemize}

  \vspace{-20pt}

\end{frame}

\begin{frame}[fragile]{Interoperating with non-Kokkos Code}
   \textbf{Sometimes your Kokkos code can't control all allocations!}

   \begin{itemize}
	   \item Obviously best to avoid that unpleasant situation ...
   \end{itemize}

   But say you use some external function like IO classes:

\begin{code}[keywords={int,vector,string,double}]
struct MatrixReader {
  int N, M;
  std::vector<double> values;
  void read_file(std::string name) {...}
};
\end{code}

\pause
	\textbf{How can you get this to the GPU without extra allocation?}

	\pause
	\begin{block}{Unmanaged Views}
	  Views can wrap existing allocations as Unmanaged Views.
	\end{block}

\end{frame}
%==========================================================================

\begin{frame}[fragile]{Unmanaged Views (0)}

  \textbf{Unmanaged View description:}

  \vspace{5pt}
  \begin{itemize}
    \item{Normally, Views allocate memory and manage.}
    \item{Instead, Views can use externally controlled memory}
    \pause
    \item{Caveats}
    \begin{itemize}
      \item{No reference counting}
      \item{No deallocation in the constructor}
      \item{No check for the correct memory space}
    \end{itemize}
    \item{Usages}
    \begin{itemize}
      \item{Layout-punning: e.g., treat multidimensional View as one-dimensional views without copying}
      \item{Use \texttt{std::vector} or memory from CUDA library, e.g. \texttt{cuSPARSE}}
    \end{itemize}
  \end{itemize}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Unmanaged Views (1)}

  \textbf{Back to our IO example:}
  \begin{code}[keywords={int,vector,string,double}]
struct MatrixReader {
  int N, M;
  std::vector<double> values;
  void read_file(std::string name) {...}
};
  \end{code}
  
  To create an unmanaged View:
  \begin{itemize}
   \item Provide a pointer as the first constructor argument.
   \item Give all the runtime dimensions.
   \item Make sure Layout and MemorySpace match!
   \item Unmanaged Views do NOT get a label!
  \end{itemize}

  \pause
  \begin{code}[keywords={View,double,LayoutRight,HostSpace,MemoryTraits,Unmanaged}]
MatrixReader reader; reader.read_file("MM");
View<double**,LayoutRight,HostSpace>
  h_a(reader.values.data(),reader.N,reader.M);
  \end{code}

  \pause
  \textbf{How do we get this to the device?}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Unmanaged Views (2)}

  \textbf{In Module 2 we learned the Mirror Pattern}
  \begin{itemize}
    \item But the mirror pattern started with a device view!
  \end{itemize}

  \pause

  \begin{block}{Mirror in any Space}
  Kokkos::create\_mirror\_view can take a space argument for location of mirror.
  \end{block}

  \pause
  \begin{code}[keywords={}]
// Create mirror into default memory space
using space_t = DefaultExecutionSpace::memory_space;
auto a = create_mirror_view(space_t(), h_a);
// Copy values from the host to the device
deep_copy(a, h_a);
  \end{code}

  \pause
\vspace{0.5cm}
  Since the ``create mirror and then copy'' pattern is common we have a shortcut:

  \begin{code}[keywords={}]
auto a = create_mirror_view_and_copy(space_t(), h_a);
  \end{code}


\end{frame}

%==========================================================================

\begin{frame}[fragile]{Scratch Allocations}
  Using pre-allocated scratch memory for temporary data structures is common to:
  \begin{itemize}
     \item Eliminate costly allocation/deallocation operations
     \item Reduce total memory footprint.
  \end{itemize}
\pause
  \begin{block}{Unmanaged Views of Scratch Allocations}
	  Unmanaged Views can be used to get arrays of different shapes backed by the same memory.
  \end{block}
   
  \begin{code}[keywords={void,View,double}]
void* scratch = kokkos_malloc<>("Scratch", scratch_size);
View<double**> a_scr(scratch, N,M);
View<int*> b_scr(scratch,K);
  \end{code}

\pause
	How much memory do you need for a \texttt{View}?

  \begin{code}[keywords={int,View,double}]
int scratch_size = View<double**>::required_allocation_size(N,M);
  \end{code}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Unmanaged Views Summary}

\vspace{-10pt}

  \begin{itemize}
    \item{Unmanaged Views wrap existing allocations} 
    \begin{itemize}
       \item{No ref-counting}
       \item{No deallocation after losing scope}
       \item{No memory space checks}
    \end{itemize}
    \pause
    \item{Unmanaged view is created with pointer and runtime dimensions }  
    \pause
  \begin{code}[keywords={}]
void* ptr = kokkos_malloc<>("Alloc", alloc_size);
View<double**> h_a((double*)ptr,N,M);
  \end{code}
  \pause
    \item {Unmanaged view uses}
    \begin{itemize}
    \item {Access externally controlled memory }
    \item {Access temporary scratch memory}
    \item {Layout pruning - view underlying data using different layout}
    \end{itemize} 
  \end{itemize}

\end{frame}
