
\begin{frame}[fragile]{}

  {\Huge Advanced Reductions}

  \vspace{20pt}

  \textbf{Learning objectives:}
  \begin{itemize}
    \item{How to use Reducers to perform different reductions.}
    \item{How to do multiple reductions in one kernel.}
    \item{Using \texttt{Kokkos::View}'s as result for asynchronicity.}
    \item{Custom reductions}
  \end{itemize}

  \vspace{-20pt}

\end{frame}

\begin{frame}[fragile]{Reducers}

\textbf{So far only "sum" reduction. What about other things?}

\textbf{Using a Reducer:}
\begin{code}[linebackgroundcolor={
          \btLstHL<2>{5}{red!20}
        }, keywords={parallel_reduce,double,Max}]
double max_value = 0;
parallel_reduce("Label", numberOfIntervals,
  KOKKOS_LAMBDA(const int64_t i, double & valueToUpdate) {
    double my_value = function(...);
    if(my_value > valueToUpdate) valueToUpdate = my_value;
}, Kokkos::Max<double>(max_value));
\end{code}

\begin{itemize}
\item<2-> Note how the operation in the body matches the reducer op!
\item<3-> The scalar type is used as a template argument.
\item<4-> Many reducers available: \texttt{Sum, Prod, Min, Max, MinLoc,} see:  {\tiny \url{https://kokkos.github.io/kokkos-core-wiki/API/core/builtin_reducers.html}}
\item<5-> Some reducers (like \texttt{MinLoc}) use special scalar types!
\item<6-> Custom value types supported via specialization of \texttt{reduction\_identity}.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Simultaneous Reductions}

\textbf{Sometimes multiple reductions are needed}

	\begin{itemize}
		\item Provide multiple reducers/result arguments
		\item Functor/Lambda operator takes matching thread-local variables
		\item Mixing scalar types is fine.
	\end{itemize}

\begin{code}[keywords={parallel_reduce,double,float,Max}]
float max_value = 0;
double sum = 0;
parallel_reduce("Label", numberOfIntervals,
    KOKKOS_LAMBDA(const int64_t i,float& tl_max,double& tl_sum){
  float a_i = a[i];
  if(a_i > tl_max) tl_max = a_i;
  tl_sum += a_i;
}, Kokkos::Max<float>(max_value),sum);
\end{code}

\end{frame}

\begin{frame}[fragile]{Views as Result arguments}

\textbf{Reducing into a Scalar is blocking!}

	\begin{itemize}
		\item Providing a reference to scalar means no lifetime expectation.
			\begin{itemize}
				\item Call to \texttt{parallel\_reduce} returns after writing the result.
			\end{itemize}
		\item \texttt{Kokkos::View} can be used as a result, allowing for potentially non-blocking execution.
		\item Can provide \texttt{View} to host memory, or to memory accessible by the \texttt{ExecutionSpace} for the reduction.
		\item Works with Reducers too!
	\end{itemize}

	\begin{code}[keywords={parallel_reduce,double,View,RangePolicy,CudaSpace,HostSpace}]
View<double,HostSpace> h_sum("sum_h");
View<double,CudaSpace> d_sum("sum_d");
using policy_t = RangePolicy<Cuda>;

parallel_reduce("Label", policy_t(0,N), SomeFunctor, 
  h_sum);

parallel_reduce("Label", policy_t(0,N), SomeFunctor, 
  Kokkos::Sum<double,CudaSpace>(d_sum));
\end{code}
\end{frame}

\begin{frame}[fragile]{Custom Reductions}
\textbf{Pseudocode for Kokkos implementation}
\begin{code}[keywords={parallel_reduce,custom}]
per_thread:
  value& tmp=init(local_tmp);
  for (i in local range)
    functor(i, tmp)
call join for merging values between threads
  in the same thread group
let one (the last) thread group merge all results
  from all thread groups
call final(result) on one thread 
\end{code}

Three ingredients
\begin{itemize}
\item init (optional), default: default constructor
\item join (required)
\item final (optional), default: no-op
\end{itemize}

\end{frame}

\begin{frame}[fragile]{Custom Reductions}
Rules for choosing reduction behavior
\begin{enumerate}
\item If a reducer is specified (return type is a functor with \texttt{reducer} alias to itself), use that.
\item If functor implements \texttt{join}, use functor as reducer.
\item Otherwise, assume \texttt{join} behaves like \texttt{operator+}.
\end{enumerate}

Note that the functor's \texttt{init}, \texttt{join}, \texttt{final} members must be tagged if the call operator is tagged. The reducers member functions must never be tagged.
\end{frame}

\begin{frame}[fragile]{Reducer Concept}
\scriptsize
\begin{code}[basicstyle=\tiny]
class Reducer {
  public:
    using reducer    = Reducer;
    using value_type = ... ;
    using result_view_type = Kokkos::View<value_type, ... >;

    KOKKOS_FUNCTION
    void join(value_type& dest, const value_type& src) const;

    //optional
    KOKKOS_INLINE_FUNCTION
    void init(value_type& val) const;
   
    //optional
    KOKKOS_INLINE_FUNCTION
    void final(value_type& val) const;

    KOKKOS_INLINE_FUNCTION
    value_type& reference() const;

    KOKKOS_INLINE_FUNCTION
    result_view_type view() const;

    KOKKOS_INLINE_FUNCTION
    Reducer(value_type& value_);

    KOKKOS_INLINE_FUNCTION
    Reducer(const result_view_type& value_);
};
\end{code}
\end{frame}
