\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-7475 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 2: Views and Spaces}

%\author{
%  Jeff Miles \inst{1},
%  Christian Trott \inst{1}
%}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories, \inst{2} Oak Ridge National Laboratory \and \inst{3} Los Alamos National Laboratory}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}
                \begin{itemize}
			\item{Slides, recording and Q\&A for the lectures}
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki}:
                \begin{itemize}
                        \item Programming guide and API reference documentation
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}{Lecture Series Outline}

\begin{itemize}
        \item Module 1: Introduction, Building and Parallel Dispatch
        \item \textbf{Module 2: Views and Spaces}
        \item Module 3: Data Structures + MultiDimensional Loops
        \item Module 4: Hierarchical Parallelism
        \item Module 5: Tasking, Streams and SIMD
        \item Module 6: Internode: MPI and PGAS
        \item Module 7: Tools: Profiling, Tuning and Debugging
        \item Module 8: Kernels: Sparse and Dense Linear Algebra
        \item Reserve Day
\end{itemize}
\end{frame}

\begin{frame}{Module 1: Summary}
	\textbf{Kokkos Ecosystem:}
	\begin{itemize}
		\item C++ Performance Portability Programming Model.
		\item The Kokkos Ecosystem provides capabilities needed for serious code development.
		\item Kokkos is supported by multiple National Laboratories with a sizeable dedicated team.
	\end{itemize}

	\textbf{Building Kokkos}
	\begin{itemize}
    \item{Kokkos's primary build system is CMAKE.}
    \item{Kokkos options are transitively passed on, including many necessary compiler options.}
    \item{The Spack package manager does support Kokkos.}
    \item{For applications with few if any dependencies, building Kokkos as part of your code is an option with CMake and GNU Makefiles.}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 1: Summary}
	\textbf{Data Parallelism:}
	\begin{itemize}
		\item Simple things stay simple!
		\item You use \textbf{parallel patterns} and \textbf{execution policies} to execute \textbf{computational bodies}
		\item Simple parallel loops use the \texttt{parallel\_for} pattern:
\begin{code}[linebackgroundcolor={\btLstHL<1->{3}{bodyColor}},frame=single]
  @patternparallel_for@pattern("Label",@policyN@policy, [=] (int64_t i) {
   /* loop body */
  });
\end{code}
\item Reductions combine contributions from loop iterations
\begin{code}[linebackgroundcolor={\btLstHL<1->{3}{bodyColor}},frame=single]
int result;
@patternparallel_reduce@pattern("Label",@policyN@policy, [=] (int64_t i, int& lres) {
   /* loop body */
    lres += /* something */
  },result);
\end{code}

\end{itemize}

	\textbf{Recording:} \url{https://bit.ly/kokkos-lecture-series-1}

\end{frame}

\begin{frame}{Module 2}
  \begin{block}{Kokkos View}
    What are Views? How to create them? Why should you use it?
  \end{block}


  \begin{block}{Memory and Execution Spaces}
    How to control where data lives and code executes.
  \end{block}

  \begin{block}{Memory Access Patterns}
    The importance of access patterns for performance portability and how to control it.
  \end{block}

  \begin{block}{Advanced Reductions}
    Going beyond just basic summation.
  \end{block}
\end{frame}  

\input{../sections/Section_Views}

\input{../sections/Section_Spaces}

\input{../sections/Section_MemoryAccessPatterns}

\input{../sections/Section_AdvancedReductions}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Kokkos View}
	\begin{itemize}
		\item Multi Dimensional Array.
		\item Compile and Runtime Dimensions.
		\item Reference counted like a \texttt{std::shared\_ptr} to an array.
	\end{itemize}
\begin{code}[keywords={View,int}]
	Kokkos::View<int*[5]> a("A", N);
	a(3,2) = 7;
\end{code}

	\textbf{Execution Spaces}
	\begin{itemize}
		\item{Parallel operations execute in a specified \textbf{Execution Space}}
		\item{Can be controlled via template argument to \textbf{Execution Policy}}
		\item{If no Execution Space is provided use \texttt{DefaultExecutionSpace}}
	\end{itemize}
\begin{code}[keywords={parallel_for,Cuda,RangePolicy}]
// Equivalent:
parallel_for("L", N, functor);
parallel_for("L",
  RangePolicy<DefaultExecutionSpace>(0, N), functor);
\end{code}
\end{frame}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Memory Spaces}
	\begin{itemize}
		\item Kokkos Views store data in \textbf{Memory Spaces}.
		\item Provided as template parameter.
		\item If no Memory Space is given, use  \texttt{Kokkos::DefaultExecutionSpace::memory\_space}.
		\item \texttt{deep\_copy} is used to transfer data: no hidden memory copies by Kokkos.
	\end{itemize}
\begin{code}[keywords={View,int,CudaSpace,create_mirror_view}]
	View<int*, CudaSpace> a("A", M);
	// View in host memory to load from file
	auto h_a = create_mirror_view(a);
        load_from_file(h_a);
	// Copy
	deep_copy(a,h_a);
\end{code}

\end{frame}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Layouts}
	\begin{itemize}
		\item Kokkos Views use an index mapping to memory determined by a \textbf{Layout}.
		\item Provided as template parameter.
		\item If no \textbf{Layout} is given, derived from the execution space associated with the memory space.
		\item Defaults are good if you parallelize over left most index!
	\end{itemize}

\begin{code}[keywords={View,int,CudaSpace}]
	View<int**, LayoutLeft> a("A", N, M);
	View<int**, LayoutRight> b("B", N, M);

	parallel_for("Fill", N, KOKKOS_LAMBDA(int i) {
          for(int j = 0; j < M; j++) {
            a(i,j) = i * 1000 + j; // coalesced
	    b(i,j) = i * 1000 + j; // cached
          }
	});
\end{code}

\end{frame}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Advanced Reductions}
	\begin{itemize}
        \item \texttt{parallel\_reduce} defaults to summation
        \item Kokkos reducers can be used to reduce over arbitrary operations
        \item Reductions over multiple values are supported
        \item Only reductions into scalar arguments are guaranteed to be synchronous
        \item Support for custom reductions
	\end{itemize}

\begin{code}[keywords={View,int,CudaSpace}]
    parallel_reduce("Join", n,
      KOKKOS_LAMBDA(int i, double& a, int& b) {
        int idx = foo();
        if(idx > b) b = idx;
        a += bar();
      }, result, Kokkos::Max<int>{my_max});
\end{code}

\end{frame}

\begin{frame}{Module 3: Outlook (07/31)}

	\vspace{10pt}
	\textbf{Advanced Data Structures}
	\begin{itemize}
        \item Subsetting and slicing of \texttt{View}s
        \item Higher-level and special purpose \texttt{View} data structures
        \item Atomic access to a \texttt{View}'s data
	\end{itemize}

	\vspace{10pt}
	\textbf{More Parallel Policies:}
	\begin{itemize}
		\item Multidimensional loops with \texttt{MDRangePolicy}
	\end{itemize}

	\vspace{10pt}
    \textbf{Slack channel:} {\scriptsize \url{https://kokkosteam.slack.com/}}
	
	\vspace{10pt}
	\textbf{Recordings/Slides:} {\scriptsize \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}}

\end{frame}

\end{document}

