\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-7475 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{The Fundamentals: A Condensed Short Tutorial}

%\author{
%  Jeff Miles \inst{1},
%  Christian Trott \inst{1}
%}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories, \inst{2} Oak Ridge National Laboratory \and \inst{3} Los Alamos National Laboratory}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories}

\input{KokkosTutorial_PostTitle}

\shorttrue
\mediumfalse
\fullfalse

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}{The Fundamentals}
	{\huge The Fundamentals}

	\textbf{A Condensed Short Tutorial}

	\vspace{10pt}
	This lecture covers fundamental concepts of Kokkos with Hands-On Exercises as homework.

	Slides: \url{https://github.com/kokkos/kokkos-tutorials/Intro-Short/KokkosTutorial_Short.pdf}

	\vspace{20pt}
	For the full lectures, with more capabilities covered, and more in-depth explanations visit:

	\url{https://github.com/kokkos/kokkos-tutorials/wiki/Kokkos-Lecture-Series}
\end{frame}

\input{../sections/Section_WhatIsKokkos}

\begin{frame}{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://github.com/kokkos/kokkos-tutorials/wiki/Kokkos-Lecture-Series}:
                \begin{itemize}
			\item{Slides, recording and Q\&A for the Full Lectures}
                \end{itemize}
        \item \url{https://kokkos.org}: Follow Documentation then Core
                \begin{itemize}
                        \item Programming guide and API references
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}

\input{../sections/Section_DataParallelPatterns}

\input{../sections/Section_Views}

\input{../sections/Section_Spaces}

\input{../sections/Section_MemoryAccessPatterns}

%\input{../sections/Section_Hierarchical}

%\begin{frame}[fragile]{Exercise: CG-Solve HP}
%
%  \textbf{Exercise}: Find $x$ in $b = A * x$
%
%  Getting set up in your home directory:
%  \begin{code}
%    mkdir Kokkos
%    cd Kokkos
%    git clone https://github.com/kokkos/kokkos
%    git clone https://github.com/kokkos/kokkos-tutorials
%  \end{code}
%
%  \vspace{5pt}
%  Find the exercise in the kokkos-tutorials/Exercises/cg-solve-hp folder.
%
%
%  \vspace{5pt}
%  The Begin subdirectory contains the code. Only cg\_solve.cpp needs modifications.
%
%  \vspace{5pt}
%  Look for EXERCISE comments to find places to modify. Note: this contains the same Exercise components as the first cg-solve. So you can just start with the solution of that and add the new things! To make it clearer they are marked as EXERCISE-HP.
%
%\end{frame}
%
%\begin{frame}[fragile]{Exercise: CG Solve HP}
%\textbf{Tasks:}
%\begin{itemize}
%  \item Use HostMirrors instead of Unified Memory for GPUs.
%  \item Use a hierarchical parallelism SPMV.
%\end{itemize}
%
%\vspace{10pt}
%\textbf{Things to try:}
%  \begin{itemize}
%  \item Compare with previous exercise on GPU with low iteration count.
%  \item Compare performance for small problems.
%  \item Compare performance dependent on Layout of col\_idx and values.
%  \end{itemize}
%\end{frame}


\begin{frame}[fragile]{What we didn't cover}
	\textbf{This was a short introduction}
	
	Didn't cover many things:
	\begin{itemize}
		\item Full build system integration.
		\item Non-Sum reductions / multiple reductions.
		\item Multidimensional loops.
                \item Hierarchical parallelism.
		\item Advanced data structures.
		\item Subviews.
		\item Atomic operations and Scatter Contribute patterns.
		\item Team Scratch memory (GPU shared memory).
		\item SIMD vectorization.
		\item MPI and PGAS integration.
		\item Tools for Profiling, Debugging and Tuning.
		\item Math Kernels.
	\end{itemize}

\end{frame}

\begin{frame}{The Kokkos Lectures}
        
	\begin{block}{The Kokkos Lectures}
		Watch the Kokkos Lectures for all of those and more in-depth explanations or do them on your own.
	\end{block}

\begin{itemize}
	\item Module 1: Introduction, Building and Parallel Dispatch
	\item Module 2: Views and Spaces
	\item Module 3: Data Structures + MultiDimensional Loops
	\item Module 4: Hierarchical Parallelism
	\item Module 5: Tasking, Streams and SIMD
	\item Module 6: Internode: MPI and PGAS
	\item Module 7: Tools: Profiling, Tuning and Debugging
	\item Module 8: Kernels: Sparse and Dense Linear Algebra
\end{itemize}

\begin{center}
\url{https://kokkos.link/the-lectures}
\end{center}

\end{frame}

\begin{frame}{Find More}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://kokkos.link/the-lectures}:
                \begin{itemize}
			\item{Slides, recording and Q\&A for the Full Lectures}
                \end{itemize}
        \item \url{https://kokkos.org}: Follow Documentation then Core
                \begin{itemize}
                        \item Programming guide and API references
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}

\end{document}

