\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-8766 PE}
\usepackage{pgfplotstable}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 6: Fortran/Python interoperability, MPI and PGAS}

%\author{
%  Jeff Miles \inst{1},
%  Christian Trott \inst{1}
%  Jan Ciesko \inst{1}
%}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories, \inst{2} Oak Ridge National Laboratory \and \inst{3} Los Alamos National Laboratory}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}[fragile]{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://github.com/kokkos/kokkos-tutorials/wiki/Kokkos-Lecture-Series}:
                \begin{itemize}
        \item{Slides, recording and Q\&A for the Lectures}
                \end{itemize}
        \item \url{https://kokkos.github.io/kokkos-core-wiki}:
                \begin{itemize}
                        \item Wiki including API reference
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}



\begin{frame}{Lecture Series Outline}

\begin{itemize}
        \item 07/17 Module 1: Introduction, Building and Parallel Dispatch
        \item 07/24 Module 2: Views and Spaces
        \item 07/31 Module 3: Data Structures + MultiDimensional Loops
        \item 08/07 Module 4: Hierarchical Parallelism
        \item 08/14 Module 5: Tasking, Streams and SIMD
        \item 08/21 \textbf{Module 6: Internode: MPI and PGAS}
        \item 08/28 Module 7: Tools: Profiling, Tuning and Debugging
        \item 09/04 Module 8: Kernels: Sparse and Dense Linear Algebra
        \item 09/11 Reserve Day
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 5 Summary}
\textbf{SIMD Types}
	\begin{itemize}
		\item{SIMD types help vectorize code.}
		\item{In particular for \textbf{outer-loop} vectorization.}
		\item{There are \textbf{storage} and \textbf{temporary} types.}
		\item{Currently considered experimental at \url{https://github.com/kokkos/simd-math}: please try it out and provide feedback.}
	\end{itemize}

\textbf{Blocking Behavior and Streams}
  \begin{itemize}
    \item{Execution Space Instances execute work in order of dispatch.}
    \item{Operations in distinct Execution Space Instances can overlap.}
    \item{Each Execution Space type has a default instance.}
    \item{Use \texttt{Kokkos::fence()} to wait for completion of ALL outstanding work or \texttt{exec\_space\_instance.fence()} to wait on work in a specific execution space instance.}
  \end{itemize}

\end{frame}


\begin{frame}{Module 6: Learning objectives}
  \begin{block}{Language Interoperability}
    \begin{itemize}
    \item Writing hybrid Fortran applications
    \item And, writing hybrid Python applications with Kokkos
  \end{itemize}
  \end{block}

  \begin{block}{Interoperability with MPI}
  \begin{itemize}
    \item Learning how to develop hybrid MPI+Kokkos applications
    \item And, how to implement overlapping communication with computation
    \item Handling buffers and sparse indexing
  \end{itemize}
  \end{block}

  \begin{block}{Interoperability with PGAS}
  \begin{itemize}
    \item How to create globally accessible Views
    \item Insight into a use-case (SPMV)
  \end{itemize}
  \end{block}
\end{frame}

\input{../sections/Section_FortranInterOp}
\input{../sections/Section_PythonInterOp}
\input{../sections/Section_MPI}
\input{../sections/Section_PGAS}

\begin{frame}{Module 6 Summary}
\textbf{Simple MPI and Kokkos Interaction is easy!}
\begin{itemize}
  \item Simply pass \texttt{data()} of a View to MPI functions plus its size.
  \begin{itemize}
    \item But it better be a contiguous View!
  \end{itemize}
  \item Initialize Kokkos after MPI, and finalize it before MPI
\end{itemize}

\vspace{10pt}
\textbf{Overlapping communication and computation possible}
\begin{itemize}
  \item Use Execution Space instances to overlap packing/unpacking with other computation.
  \item Order operations to maximize overlapping potential. 
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 6 Summary}
\textbf{Fortran Language Compatibility Layer}
\begin{itemize}
  \item Initialize Kokkos from Fortran via \texttt{kokkos\_initialize} and \texttt{kokkos\_finalize}
  \item \texttt{nd\_array\_t} is a representation of a \texttt{Kokkos::View}
  \item Create \texttt{nd\_array\_t} from a Fortran array via \texttt{to\_nd\_array}
  \item Allocate \texttt{Kokkos::DualView} in Fortran with \texttt{kokkos\_allocate\_dualview}
\end{itemize}


  \vspace{10pt}
  \textbf{The Python Interop}
  \begin{itemize}
    \item Initialize and Finalize Kokkos from Python
    \item Create Views from Python
    \item Alias Kokkos Views with NumPy arrays
    \item \textbf{This is in pre-release: ask us for access.}
  \end{itemize}
\end{frame}

\begin{frame}{Module 7: Outlook (08/28)}
    \vspace{-3pt}
	\textbf{Clang-Tidy Static Analysis}
	\begin{itemize}
        \item {Getting Kokkos specific warnings in your IDE}
	\end{itemize}
	
	\vspace{5pt}
	\textbf{Kokkos Tools}
	\begin{itemize}
		\item {Debugging}
		\item {Profiling}
                \item {Tuning}
	\end{itemize}

	\vspace{5pt}
	\textbf{Custom and 3rd party tools}
	\begin{itemize}
		\item {How to write distributed code using a global arrays like interface}
	\end{itemize}

	\vspace{5pt}
	\textbf{Don't Forget:} Join our Slack Channel and drop into our office hours on Tuesday.
	
	\vspace{5pt}
	\textbf{Updates at:} \href{https://kokkos.link/the-lectures-updates}{kokkos.link/the-lectures-updates}
	
	\vspace{5pt}
	\textbf{Recordings/Slides:} \href{https://kokkos.link/the-lectures}{kokkos.link/the-lectures}

\end{frame}

\end{document}

