\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-9031 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 7: Kokkos Tools}


\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}[fragile]{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://github.com/kokkos/kokkos-tutorials/wiki/Kokkos-Lecture-Series}:
                \begin{itemize}
			\item{Slides, recording and Q\&A for the Lectures}
                \end{itemize}
        \item \url{https://kokkos.github.io/kokkos-core-wiki}:
                \begin{itemize}
                        \item Wiki including API reference
                \end{itemize}
        \item \url{https://github.com/kokkos/kokkos-tools/wiki}:
                \begin{itemize}
                        \item Kokkos Tools Wiki
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}[fragile]{Lecture Series Outline}

\begin{itemize}
        \item 07/17 Module 1: Introduction, Building and Parallel Dispatch
        \item 07/24 Module 2: Views and Spaces
        \item 07/31 Module 3: Data Structures + MultiDimensional Loops
        \item 08/07 Module 4: Hierarchical Parallelism
        \item 08/14 Module 5: Tasking, Streams and SIMD
        \item 08/21 Module 6: Internode: MPI and PGAS
        \item \textbf{08/28 Module 7: Tools: Profiling, Tuning and Debugging}
        \item 09/04 Module 8: Kernels: Sparse and Dense Linear Algebra
        \item 09/11 Reserve Day
\end{itemize}

\end{frame}

\begin{frame}{Module 6 Summary}
\textbf{Simple MPI and Kokkos Interaction is easy!}
\begin{itemize}
  \item Simply pass \texttt{data()} of a View to MPI functions plus its size.
  \begin{itemize}
    \item But it better be a contiguous View!
  \end{itemize}
  \item Initialize Kokkos after MPI, and finalize it before MPI
\end{itemize}

\vspace{10pt}
\textbf{Overlapping communication and computation possible}
\begin{itemize}
  \item Use Execution Space instances to overlap packing/unpacking with other computation.
  \item Order operations to maximize overlapping potential. 
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 6 Summary}
\textbf{Fortran Language Compatibility Layer}
\begin{itemize}
  \item Initialize Kokkos from Fortran via \texttt{kokkos\_initialize} and \texttt{kokkos\_finalize}
  \item \texttt{nd\_array\_t} is a representation of a \texttt{Kokkos::View}
  \item Create \texttt{nd\_array\_t} from a Fortran array via \texttt{to\_nd\_array}
  \item Allocate \texttt{Kokkos::DualView} in Fortran with \texttt{kokkos\_allocate\_dualview}
\end{itemize}


  \vspace{10pt}
  \textbf{The Python Interop}
  \begin{itemize}
    \item Initialize and Finalize Kokkos from Python
    \item Create Views from Python
    \item Alias Kokkos Views with NumPy arrays
    \item \textbf{This is in pre-release: ask us for access.}
  \end{itemize}
\end{frame}

\begin{frame}{Module 7: Learning objectives}
  \begin{block}{Simple Tools Usage}
    \begin{itemize}
    \item How to dynamically load a Kokkos Tool.
    \item Simple Profiling and Debugging.
    \item Leveraging the KokkosP instrumentation for third party tools.
  \end{itemize}
  \end{block}

  \begin{block}{Kokkos Tuning}
  \begin{itemize}
    \item Learn to auto-tune runtime parameters.
  \end{itemize}
  \end{block}

  \begin{block}{Build Your Own Tool}
  \begin{itemize}
    \item Learn how to build your own tools.
  \end{itemize}
  \end{block}

  \begin{block}{Leveraging Static Analysis}
  \begin{itemize}
    \item How to use Kokkos' LLVM tools for static analysis.
  \end{itemize}
  \end{block}
\end{frame}

\input{../sections/Section_Tools_Simple}
\input{../sections/Section_Tools_Connectors}
%\input{../sections/Section_Tools_QuickStart}
\input{../sections/Section_Tools_Tuning}
\input{../sections/Section_Tools_Custom}
\input{../sections/Section_Tools_ClangSA}

\begin{frame}[fragile]{Module 7: Summary}

\textbf{Kokkos Tools:}
\begin{itemize}
  \item Kokkos Tools provide an instrumentation interface \textbf{KokkosP} and \textbf{Tools} to leverage it.
  \item The interface is \textbf{always available} - even in release builds.
  \item Zero overhead if no tool is loaded during the run.
  \item Dynamically load a tool via setting \texttt{KOKKOS\_TOOLS\_LIBS} environment variable.
  \item Set callbacks in code for tools compiled into the executable. 
\end{itemize}

\textbf{Kokkos Connector Tools:}
\begin{itemize}
  \item Connectors inject Kokkos specific information into vendor and academic tools.
  \item Helps readability of profiles.
  \item Removes need to put vendor specific instrumentation in codes.
  \item Growing list of tools support Kokkos natively.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 7: Summary}
\textbf{Kokkos Tuning Hooks enable more performance portability}
\begin{itemize}
  \item Avoid figuring out the right heuristic for every platform.
  \item Input variables descripte the problem scope.
  \item Output variables descripe the search space.
\end{itemize}

\textbf{Implementing your own tools is easy!}
\begin{itemize}
  \item Simply implement the needed C callback functions.
  \item Only implement what you need.
  \item The callback registration system allows to embed tools in applications.
\end{itemize}

\textbf{Static Analysis}
\begin{itemize}
  \item Have semantic checks going beyond C++ errors.
  \item Integrates into your editors.
\end{itemize}
\end{frame}

\begin{frame}{Module 8: Outlook (09/04)}
	\textbf{KokkosKernels Dense Linear Algebra}

	\textbf{KokkosKernels Sparse Linear Algebra}

	\textbf{KokkosKernels Sparse Solvers}

	\textbf{KokkosKernels Graph Kernels}


	\vspace{5pt}
	\textbf{Don't Forget:} Join our Slack Channel and drop into our office hours on Tuesday.
	
	\vspace{5pt}
	\textbf{Updates at:} \href{https://kokkos.link/the-lectures-updates}{kokkos.link/the-lectures-updates}
	
	\vspace{5pt}
	\textbf{Recordings/Slides:} \href{https://kokkos.link/the-lectures}{kokkos.link/the-lectures}

\end{frame}
\end{document}

