\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-9315 TR}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 8: Kokkos Kernels Math Library}


\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}[fragile]{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://github.com/kokkos/kokkos-tutorials/wiki/Kokkos-Lecture-Series}:
                \begin{itemize}
			\item{Slides, recording and Q\&A for the Lectures}
                \end{itemize}
        \item \url{https://kokkos.github.io/kokkos-core-wiki}:
                \begin{itemize}
                        \item Wiki including API reference
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}[fragile]{Lecture Series Outline}

\begin{itemize}
        \item 07/17 Module 1: Introduction, Building and Parallel Dispatch
        \item 07/24 Module 2: Views and Spaces
        \item 07/31 Module 3: Data Structures + MultiDimensional Loops
        \item 08/07 Module 4: Hierarchical Parallelism
        \item 08/14 Module 5: Tasking, Streams and SIMD
        \item 08/21 Module 6: Internode: MPI and PGAS
        \item 08/28 Module 7: Tools: Profiling, Tuning and Debugging
        \item \textbf{09/04 Module 8: Kernels: Sparse and Dense Linear Algebra}
\end{itemize}

\end{frame}

\begin{frame}[fragile]{Module 7: Summary}

\textbf{Kokkos Tools:}
\begin{itemize}
  \item Kokkos Tools provide an instrumentation interface \textbf{KokkosP} and \textbf{Tools} to leverage it.
  \item The interface is \textbf{always available} - even in release builds.
  \item Zero overhead if no tool is loaded during the run.
  \item Dynamically load a tool via setting \texttt{KOKKOS\_TOOLS\_LIBS} environment variable.
  \item Set callbacks in code for tools compiled into the executable. 
\end{itemize}

\textbf{Kokkos Connector Tools:}
\begin{itemize}
  \item Connectors inject Kokkos specific information into vendor and academic tools.
  \item Helps readability of profiles.
  \item Removes need to put vendor specific instrumentation in codes.
  \item Growing list of tools support Kokkos natively.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 7: Summary}
\textbf{Kokkos Tuning Hooks enable more performance portability}
\begin{itemize}
  \item Avoid figuring out the right heuristic for every platform.
  \item Input variables descripte the problem scope.
  \item Output variables descripe the search space.
\end{itemize}

\textbf{Implementing your own tools is easy!}
\begin{itemize}
  \item Simply implement the needed C callback functions.
  \item Only implement what you need.
  \item The callback registration system allows to embed tools in applications.
\end{itemize}

\textbf{Static Analysis}
\begin{itemize}
  \item Have semantic checks going beyond C++ errors.
  \item Integrates into your editors.
\end{itemize}
\end{frame}

\input{../sections/Section_KokkosKernels_INTRO}

\begin{frame}[fragile]{Module 8: Kernels Math Libraries (09/04)}

	\vspace{3pt}
	\textbf{Dense Linear Algebra (BLAS and Batched BLAS)}
	\begin{itemize}
        \item Motivation for BLAS/LAPACK functions
        \item Algorithm Specialization for Applications
        \item Calling BLAS/LAPACK functions
	\end{itemize}

	\vspace{3pt}
	\textbf{Sparse Linear Algebra}
	\begin{itemize}
        \item Sparse Containers (CrsMatrix, StaticCrsGraph, Vector)
        \item Sparse Matrix-Vector Multiplication (SpMV)
        \item Sparse Matrix-Matrix Addition (SpADD)
        \item Sparse Matrix-Matrix Multiplication (SpGEMM)
	\end{itemize}

  \vspace{3pt}
  \textbf{Graph Kernels}
  \begin{itemize}
        \item Distance-1 Graph Coloring
        \item Distance-2 Graph Coloring
        \item Bipartite Graph Partial Coloring
  \end{itemize}

\end{frame}

\begin{frame}[fragile]{Module 8: Kernels Math Libraries (09/04)}

	\vspace{3pt}
	\textbf{Sparse Solvers}
	\begin{itemize}
        \item Multicolor Gauss Seidel
        \item Cluster Gauss Seidel
        \item Two-Stage Gauss Seidel
        \item Sparse Incomplete LU Factorization (SpILUK)
        \item Sparse Triangular Solver (SpTRSV)
	\end{itemize}

	\vspace{3pt}
	\textbf{Build System}
	\begin{itemize}
        \item Using Kokkos Kernels in Your Project
        \item Configure, Build, and Install Kokkos Kernels
        \item Install with Spack
	\end{itemize}

\end{frame}


\input{../sections/Section_KokkosKernels_BLAS}
\input{../sections/Section_KokkosKernels_BATCHED}
\input{../sections/Section_KokkosKernels_SPARSE}
\input{../sections/Section_KokkosKernels_GRAPH}
\input{../sections/Section_KokkosKernels_SPARSE_SOLVERS}
\input{../sections/Section_KokkosKernels_Build}

\begin{frame}[fragile]{Module 8: Summary}
  \textbf{Summary}
	\begin{itemize}
    \item Kokkos Kernels provides several performance portable dense, sparse, and graph kernels
    \item Working actively with vendors to incorporate algorithms in optimized vendor libraries and provide interface to them
    \item Kokkos Core, Kokkos Kernels, and Kokkos tools allows Kokkos ecosystem to be a complete solution for CSE applications
    \item Working actively with applications to address unique use cases
    \item Use slack/github/e-mail to reach out to us
	\end{itemize}
\end{frame}

\input{../sections/Section_LectureConclusion}
\end{document}

