\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-8508 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 5: SIMD, Streams and Tasking}

%\author{
%  Jeff Miles \inst{1},
%  Christian Trott \inst{1}
%}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories, \inst{2} Oak Ridge National Laboratory \and \inst{3} Los Alamos National Laboratory}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}
                \begin{itemize}
			\item{Slides, recording and Q\&A for the lectures}
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki}:
                \begin{itemize}
                        \item Programming guide and API reference documentation
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}[fragile]{Lecture Series Outline}

\begin{itemize}
        \item 07/17 Module 1: Introduction, Building and Parallel Dispatch
        \item 07/24 Module 2: Views and Spaces
        \item 07/31 Module 3: Data Structures + MultiDimensional Loops
        \item 08/07 Module 4: Hierarchical Parallelism
        \item \textbf{08/14 Module 5: SIMD, Streams and Tasking}
        \item 08/21 Module 6: Internode: MPI and PGAS
        \item 08/28 Module 7: Tools: Profiling, Tuning and Debugging
        \item 09/04 Module 8: Kernels: Sparse and Dense Linear Algebra
        \item 09/11 Reserve Day
\end{itemize}

\end{frame}



\begin{frame}[fragile]{Module 4: Summary}
	\textbf{Hierarchal Parallelism}
  \begin{itemize}
    \item{\textbf{Hierarchical work} can be parallelized via hierarchical parallelism.}
    \item{Hierarchical parallelism is leveraged using \textbf{thread teams} launched with a \texttt{TeamPolicy}.}
    \item{Team ``worksets'' are processed by a team in nested \texttt{parallel\_for} (or \texttt{reduce} or \texttt{scan}) calls with a \texttt{TeamThreadRange} and \texttt{ThreadVectorRange} policy.}
    \item{Execution can be restricted to a subset of the team with the \texttt{single} pattern using either a \texttt{PerTeam} or \texttt{PerThread} policy.}
    \item{Teams can be used to \textbf{reduce contention} for global resources even in ``flat'' algorithms.}
  \end{itemize}


  
\end{frame}

\begin{frame}[fragile]{Module 4: Summary}
   \textbf{Scratch Space}
\begin{itemize}
    \item{\textbf{Scratch Memory} can be use with the \texttt{TeamPolicy} to provide thread or team \textbf{private} memory.}
    \item{Usecase: per work-item temporary storage or manual caching.}
    \item{Scratch memory exposes on-chip user managed caches (e.g. on NVIDIA GPUs)}
    \item{The size must be determined before launching a kernel.}
    \item{Two levels are available: large/slow and small/fast.}
  \end{itemize}
  \textbf{Unique Token}
  \begin{itemize}
    \item{\textbf{UniqueToken} give a thread safe portable way to divide thread specific resources}
    \item{\textbf{UniqueToken} can be sized to restrict ids to a range.}
    \item{A \textbf{Global} UniqueToken is available.}
  \end{itemize}

\end{frame}

\begin{frame}{Module 5}
  \begin{block}{SIMD}
    How to vectorize code with explicit vector types.
  \end{block}

  \begin{block}{Blocking behavior and Execution Space Instances}
    What is Kokkos's blocking behavior and Execution Space Instances
  \end{block}

  \begin{block}{Tasking}
    Writing dynamic task graphs.
  \end{block}
\end{frame}

\input{../sections/Section_SIMD}
\input{../sections/Section_Streams}
\input{../sections/Section_Tasking}

\begin{frame}[fragile]{Module 5 Summary}
\textbf{SIMD Types}
	\begin{itemize}
		\item{SIMD types help vectorize code.}
		\item{In particular for \textbf{outer-loop} vectorization.}
		\item{There are \textbf{storage} and \textbf{temporary} types.}
		\item{Currently considered experimental at \url{https://github.com/Kokkos/simd-math}: please try it out and provide feedback.}
	\end{itemize}

\textbf{Blocking Behavior and Streams}
  \begin{itemize}
    \item{Execution Space Instances execute work in order of dispatch.}
    \item{Operations in distinct Execution Space Instances can overlap.}
    \item{Each Execution Space type has a default instance.}
    \item{Use \texttt{Kokkos::fence()} to wait for completion of ALL outstanding work or \texttt{exec\_space\_instance.fence()} to wait on work in a specific execution space instance.}
  \end{itemize}

\end{frame}

\begin{frame}{Module 6: Outlook (08/21)}
    \vspace{-3pt}
	\textbf{Python and Fortran Data Interoperability}
	\begin{itemize}
        \item {How to pass data back and forth between C++ Kokkos and Python/Fortran}
	\end{itemize}
	
	\vspace{5pt}
	\textbf{Kokkos + MPI: how to make it work}
	\begin{itemize}
		\item {Basic usage}
		\item {Performance considerations}
	\end{itemize}

	\vspace{5pt}
	\textbf{PGAS: Global Arrays via Kokkos}
	\begin{itemize}
		\item {How to write distributed code using a global arrays like interface}
	\end{itemize}

	\vspace{5pt}
	\textbf{Don't Forget:} Join our Slack Channel and drop into our office hours on Tuesday.
	
	\vspace{5pt}
	\textbf{Updates at:} \href{https://kokkos.link/the-lectures-updates}{kokkos.link/the-lectures-updates}
	
	\vspace{5pt}
	\textbf{Recordings/Slides:} \href{https://kokkos.link/the-lectures}{kokkos.link/the-lectures}

\end{frame}

\end{document}

