\input{KokkosTutorial_PreTitle}

%disclaimer for Sandia. uncomment and the whole blob goes awa @ 50e13125ad7dby
\def\sandid{SAND2020-7263 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}
\subtitle{Module 1: Introduction, Building and Parallel Executions}

%BAD misuse of author field
\author{Module 1: Introduction, Building and Parallel Dispatch}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\input{../sections/Section_LectureOverview}

\input{../sections/Section_WhatIsKokkos}

\input{../sections/Section_Introduction}

\input{../sections/Section_Kokkos}

\input{../sections/Section_DataParallelPatterns}

\input{../sections/Section_Building}

\begin{frame}{Module 1: Summary}
	\textbf{Kokkos Ecosystem:}
	\begin{itemize}
		\item C++ Performance Portability Programming Model.
		\item The Kokkos Ecosystem provides capabilities needed for serious code development.
		\item Kokkos is supported by multiple National Laboratories with a sizeable dedicated team.
	\end{itemize}

	\textbf{Building Kokkos}
	\begin{itemize}
    \item{Kokkos' primary build system is CMAKE.}
    \item{Kokkos options are transitively passed on, including many necessary compiler options.}
    \item{The Spack package manager does support Kokkos.}
    \item{For applications with few if any dependencies, building Kokkos as part of your code is an option with CMake and GNU Makefiles.}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 1: Summary}
	\textbf{Data Parallelism:}
	\begin{itemize}
		\item Simple things stay simple!
		\item You use \textbf{parallel patterns} and \textbf{execution policies} to execute \textbf{computational bodies}
		\item Simple parallel loops use the \texttt{parallel\_for} pattern:
\begin{code}[linebackgroundcolor={\btLstHL<1->{3}{bodyColor}},frame=single]
  @patternparallel_for@pattern("Label",@policyN@policy, [=] (int64_t i) {
   /* loop body */
  });
\end{code}
\item Reductions combine contributions from loop iterations
\begin{code}[linebackgroundcolor={\btLstHL<1->{3}{bodyColor}},frame=single]
int result;
@patternparallel_reduce@pattern("Label",@policyN@policy, [=] (int64_t i, int& lres) {
   /* loop body */
    lres += /* something */
  },result);
\end{code}
\end{itemize}

\end{frame}


\begin{frame}{Module 2: Outlook (07/24)}

	\vspace{10pt}
	\textbf{Kokkos::View:}
	\begin{itemize}
		\item Solving the data-layout issue.
		\item Controlling data life-time.
	\end{itemize}

	\vspace{10pt}
	\textbf{Execution and Memory Spaces:}
	\begin{itemize}
		\item How to control where data lives.
		\item How to control where code executes.
		\item How to manage data transfers.
	\end{itemize}

	\vspace{10pt}
    \textbf{Slack channel:} {\scriptsize \url{https://kokkosteam.slack.com/}}
	
	\vspace{10pt}
	\textbf{Recordings/Slides:} {\scriptsize \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}}

\end{frame}

\end{document}

