
\input{KokkosTutorial_PreTitle}
\def\sandid{SAND2020-9315 TR}


\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 9: Kokkos-Fortran-Interop}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumfalse
\fullfalse
\notoverviewtrue

\usepackage{minted}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}[fragile]{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://github.com/kokkos/kokkos-tutorials/wiki/Kokkos-Lecture-Series}:
                \begin{itemize}
        \item{Slides, recording and Q\&A for the Lectures}
                \end{itemize}
        \item \url{https://kokkos.github.io/kokkos-core-wiki}:
                \begin{itemize}
                        \item Wiki including API reference
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}

\input{../sections/Section_FortranInterOp}

\begin{frame}{Module 9 Summary}
\textbf{Fortran Language Compatibility Layer}
\begin{itemize}
  \item Initialize Kokkos from Fortran via \texttt{kokkos\_initialize} and \texttt{kokkos\_finalize}
  \item \texttt{nd\_array\_t} is a representation of a \texttt{Kokkos::View}
  \item Create \texttt{nd\_array\_t} from a Fortran array via \texttt{to\_nd\_array}
  \item Allocate \texttt{Kokkos::DualView} in Fortran with \texttt{kokkos\_allocate\_dualview}
\end{itemize}
\end{frame}

\begin{frame}{Disclaimers}

\begin{block}{}\small
Sandia National Laboratories is a multi-mission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC., a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy’s National Nuclear Security Administration under contract DE-NA0003525.\newline
\sandid
\end{block}

\begin{block}{}
The U.S. Department of Energy supported this work through the Los Alamos National Laboratory. Los Alamos National Laboratory is operated by Triad National Security, LLC, for the National Nuclear Security Administration of the U.S. Department of Energy (Contract No. 89233218CNA000001). Approved for public release with LA-UR-26-24642. 
\end{block}

\end{frame}

\end{document}
