\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-7908 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 3: MultiDimensional Loops and Data Structures}

%\author{
%  Jeff Miles \inst{1},
%  Christian Trott \inst{1}
%}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories, \inst{2} Oak Ridge National Laboratory \and \inst{3} Los Alamos National Laboratory}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://kokkos.github.io/kokkos-core-wiki}
                \begin{itemize}
			\item{Slides, recording and Q\&A for the Lectures}
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki}:
                \begin{itemize}
                        \item Wiki including API reference
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}{Lecture Series Outline}

\begin{itemize}
        \item 07/17 Module 1: Introduction, Building and Parallel Dispatch
        \item 07/24 Module 2: Views and Spaces
	\item \textbf{07/31 Module 3: Data Structures + MultiDimensional Loops}
        \item 08/07 Module 4: Hierarchical Parallelism
        \item 08/14 Module 5: Tasking, Streams and SIMD
        \item 08/21 Module 6: Internode: MPI and PGAS
        \item 08/28 Module 7: Tools: Profiling, Tuning and Debugging
        \item 09/04 Module 8: Kernels: Sparse and Dense Linear Algebra
        \item 09/11 Reserve Day
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Module 1: Summary}
	\textbf{Kokkos Ecosystem}

	\textbf{Building Kokkos}

	\textbf{Data Parallelism:}

	\begin{itemize}
		\item Simple parallel loops use the \texttt{parallel\_for} pattern:
\begin{code}[linebackgroundcolor={\btLstHL<1->{3}{bodyColor}},frame=single]
@patternparallel_for@pattern("Label",@policyN@policy, [=] (int64_t i) {
  /* loop body */
});
\end{code}
\item Reductions combine contributions from loop iterations
\begin{code}[linebackgroundcolor={\btLstHL<1->{3}{bodyColor}},frame=single]
int result;
@patternparallel_reduce@pattern("Label",@policyN@policy, [=] (int64_t i, int& lres) {
   /* loop body */
    lres += /* something */
  },result);
\end{code}

\end{itemize}

	\textbf{Recording:} \url{https://bit.ly/kokkos-lecture-series-1}

\end{frame}



\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Kokkos View}
	\begin{itemize}
		\item Multi Dimensional Array.
		\item Compile and Runtime Dimensions.
		\item Reference counted like a \texttt{std::shared\_ptr} to an array.
	\end{itemize}
\begin{code}[keywords={View,int}]
	Kokkos::View<int*[5]> a("A", N);
	a(3,2) = 7;
\end{code}

	\textbf{Execution Spaces}
	\begin{itemize}
		\item{Parallel operations execute in a specified \textbf{Execution Space}}
		\item{Can be controlled via template argument to \textbf{Execution Policy}}
		\item{If no Execution Space is provided use \texttt{DefaultExecutionSpace}}
	\end{itemize}
\begin{code}[keywords={parallel_for,Cuda,RangePolicy}]
// Equivalent:
parallel_for("L", N, functor);
parallel_for("L",
  RangePolicy<DefaultExecutionSpace>(0, N), functor);
\end{code}
\end{frame}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Memory Spaces}
	\begin{itemize}
		\item Kokkos Views store data in \textbf{Memory Spaces}.
		\item Provided as template parameter.
		\item If no Memory Space is given, use  \texttt{Kokkos::DefaultExecutionSpace::memory\_space}.
		\item \texttt{deep\_copy} is used to transfer data: no hidden memory copies by Kokkos.
	\end{itemize}
\begin{code}[keywords={View,int,CudaSpace,create_mirror_view}]
	View<int*, CudaSpace> a("A", M);
	// View in host memory to load from file
	auto h_a = create_mirror_view(a);
        load_from_file(h_a);
	// Copy
	deep_copy(a,h_a);
\end{code}

\end{frame}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Layouts}
	\begin{itemize}
		\item Kokkos Views use an index mapping to memory determined by a \textbf{Layout}.
		\item Provided as template parameter.
		\item If no \textbf{Layout} is given, derived from the execution space associated with the memory space.
		\item Defaults are good if you parallelize over left most index!
	\end{itemize}

\begin{code}[keywords={View,int,CudaSpace}]
	View<int**, LayoutLeft> a("A", N, M);
	View<int**, LayoutRight> b("B", N, M);

	parallel_for("Fill", N, KOKKOS_LAMBDA(int i) {
          for(int j = 0; j < M; j++) {
            a(i,j) = i * 1000 + j; // coalesced
	    b(i,j) = i * 1000 + j; // cached
          }
	});
\end{code}

\end{frame}

\begin{frame}[fragile]{Module 2: Summary}
	\textbf{Advanced Reductions}
	\begin{itemize}
        \item \texttt{parallel\_reduce} defaults to summation
        \item Kokkos reducers can be used to reduce over arbitrary operations
        \item Reductions over multiple values are supported
        \item Only reductions into scalar arguments are guaranteed to be synchronous
        \item Support for custom reductions
	\end{itemize}

\begin{code}[keywords={View,int,CudaSpace}]
    parallel_reduce("Join", n,
      KOKKOS_LAMBDA(int i, double& a, int& b) {
        int idx = foo();
        if(idx > b) b = idx;
        a += bar();
      }, result, Kokkos::Max<int>{my_max});
\end{code}

\end{frame}

\begin{frame}{Module 3}
  \begin{block}{MultiDimensional Loops}
    How to parallelize tightly nested loops using the MDRangePolicy?
  \end{block}

  \begin{block}{Subviews and Unmanaged Views}
    How to get slices of Views, View assignment rules and interoperating with external memory.
  \end{block}

  \begin{block}{Atomic Data Access}
    Using atomic functions. Implement an optimal scatter contribute pattern.
  \end{block}

  \begin{block}{DualView}
    Managing data synchronization without global understanding of data flow.
  \end{block}
\end{frame}

\input{../sections/Section_MDRangePolicy}
\input{../sections/Section_Subviews}
\input{../sections/Section_UnmanagedViews}
\input{../sections/Section_Atomics}
\input{../sections/Section_DualViews}

\begin{frame}[fragile]{Module 3: Summary}

	\textbf{MDRangePolicy}
        \begin{itemize}
                \item Tightly nested loops (similar to OpenMP collapse clause)
                \item Available with \texttt{parallel\_for} and \texttt{parallel\_reduce}
                \item Tiling strategy over the iteration space
                \item Control iteration pattern at compile time
        \end{itemize}

\begin{code}[keywords={double,Iterate,Left,Right,int,MDRangePolicy,Rank}]
View<double**,LayoutLeft> A("A",N0,N1);
parallel_for("Label",
  MDRangePolicy<Rank<2,Iterate::Left,Iterate::Left>>(
	{0,0},{N0,N1}),
  KOKKOS_LAMBDA(int i, int j) {
    A(i,j) = 1000.0 * i + 1.0*j;
});
\end{code}

\end{frame}

\begin{frame}[fragile]{Module 3: Summary}

	\textbf{Subviews}
        \begin{itemize}
                \item Taking slices of Views
                \item Similar capability as provided by Matlab, Fortran, or Python
                \item {Prefer the use of \texttt{auto} for the type
\begin{code}[keywords={View,int,subview,ALL,make_pair}]
View<int ***> v("v", N0, N1, N2);
auto sv = subview(v, i0, ALL, make_pair(start,end));
\end{code}}
        \end{itemize}

        \vspace{10pt}
        \textbf{Unmanaged Views}
        \begin{itemize}
                \item Interoperability with externally allocated arrays
                \item No reference counting, memory not deallocated at destruction
                \item { User is responsible for insuring proper dynamic and/or static extents, MemorySpace, Layout, etc.
\begin{code}[keywords={View, float, LayoutRight, HostSpace, MemoryTraits, Unmanaged}]
View<float**, LayoutRight, HostSpace>
  v_unmanaged(raw_ptr, N0, N1);
\end{code}}
        \end{itemize}

\end{frame}

\begin{frame}[fragile]{Module 3: Summary}

	\textbf{Atomic operations}
        \begin{itemize}
                \item Atomic functions available on the host or the device (e.g. \texttt{Kokkos::atomic\_add})
                \item {Use \texttt{Atomic} memory trait for atomic accesses on Views
\begin{code}[keywords={View,int,MemoryTraits,Atomic}]
View<int*> v("v", N0);
View<int*, MemoryTraits<Atomic>> v_atomic = v;
\end{code}}
                \item Use \texttt{ScatterView} for scatter-add parallel pattern
        \end{itemize}

        \vspace{10pt}
	\textbf{Dual Views}
        \begin{itemize}
                \item For managing data synchronization between host and device
 		\item Helps in codes with no holistic view of data flow
		\begin{itemize}
                   \item In particular when porting codes incrementally
                \end{itemize}
        \end{itemize}

\end{frame}
\begin{frame}{Module 4: Hierarchical Parallelism (08/07)}

	\vspace{5pt}
	\textbf{Hierarchical Parallelism}
	\begin{itemize}
        \item How to leverage more parallelism through nested loops.
        \item The concept of Thread-Teams and Vectorlength.
	\end{itemize}

	\vspace{5pt}
	\textbf{Scratch Space}
	\begin{itemize}
        \item Getting temporary workspace in kernels.
        \item Leveraging GPU Shared Memory.
	\end{itemize}

        \vspace{5pt}
        \textbf{Unique Token}
        \begin{itemize}
        \item How to acquire safely per-thread resources.
        \end{itemize}

	\vspace{10pt}
    \textbf{Slack channel:} {\scriptsize \url{https://kokkosteam.slack.com/}}
	
	\vspace{10pt}
	\textbf{Recordings/Slides:} {\scriptsize \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}}

\end{frame}

\end{document}

