\input{KokkosTutorial_PreTitle}
%disclaimer for Sandia. uncomment and the whole blob goes away @ b80c116300122
\def\sandid{SAND2020-7475 PE}

% \title{Performance Portability with Kokkos}
\title{The Kokkos Lectures}

%BAD misuse of author field
\author{Module 4: Hierarchical Parallelism}

%\author{
%  Jeff Miles \inst{1},
%  Christian Trott \inst{1}
%}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories, \inst{2} Oak Ridge National Laboratory \and \inst{3} Los Alamos National Laboratory}
%\institute[shortinst]{\tiny \inst{1} Sandia National Laboratories}

\input{KokkosTutorial_PostTitle}

\shortfalse
\mediumtrue
\fulltrue
\notoverviewtrue

\begin{document}

% \begin{frame}
%   \titlepage
% \end{frame}
% \input{sections/Section_nvlabs}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}[fragile]{Welcome to Kokkos}

\textbf{Online Resources}:

\begin{itemize}
        \item \url{https://github.com/kokkos}:
                \begin{itemize}
                        \item Primary Kokkos GitHub Organization
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}
                \begin{itemize}
			\item{Slides, recording and Q\&A for the Lectures}
                \end{itemize}
        \item \url{https://kokkos.org/kokkos-core-wiki}:
                \begin{itemize}
                        \item Programming guide and API reference documentation
                \end{itemize}
        \item \url{https://kokkosteam.slack.com}:
                \begin{itemize}
                        \item Slack channel for Kokkos.
                        \item Please join: fastest way to get your questions answered.
                        \item Can whitelist domains, or invite individual people.
                \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}[fragile]{Lecture Series Outline}

\begin{itemize}
        \item 07/17 Module 1: Introduction, Building and Parallel Dispatch
        \item 07/24 Module 2: Views and Spaces
        \item 07/31 Module 3: Data Structures + MultiDimensional Loops
        \item \textbf{08/07 Module 4: Hierarchical Parallelism}
        \item 08/14 Module 5: Tasking, Streams and SIMD
        \item 08/21 Module 6: Internode: MPI and PGAS
        \item 08/28 Module 7: Tools: Profiling, Tuning and Debugging
        \item 09/04 Module 8: Kernels: Sparse and Dense Linear Algebra
        \item 09/11 Reserve Day
\end{itemize}

\end{frame}

\begin{frame}[fragile]{Module 3: Summary}

	\textbf{MDRangePolicy}
        \begin{itemize}
                \item Tightly nested loops (similar to OpenMP collapse clause)
                \item Available with \texttt{parallel\_for} and \texttt{parallel\_reduce}
                \item Tiling strategy over the iteration space
                \item Control iteration pattern at compile time
        \end{itemize}

\begin{code}[keywords={double,Iterate,Left,Right,int,MDRangePolicy,Rank}]
View<double**,LayoutLeft> A("A",N0,N1);
parallel_for("Label",
  MDRangePolicy<Rank<2,Iterate::Left,Iterate::Left>>(
	{0,0},{N0,N1}),
  KOKKOS_LAMBDA(int i, int j) {
    A(i,j) = 1000.0 * i + 1.0*j;
});
\end{code}

\end{frame}

\begin{frame}[fragile]{Module 3: Summary}

	\textbf{Subviews}
        \begin{itemize}
                \item Taking slices of Views
                \item Similar capability as provided by Matlab, Fortran, or Python
                \item {Prefer the use of \texttt{auto} for the type
\begin{code}[keywords={View,int,subview,ALL,make_pair}]
View<int ***> v("v", N0, N1, N2);
auto sv = subview(v, i0, ALL, make_pair(start,end));
\end{code}}
        \end{itemize}

        \vspace{10pt}
        \textbf{Unmanaged Views}
        \begin{itemize}
                \item Interoperability with externally allocated arrays
                \item No reference counting, memory not deallocated at destruction
                \item { User is responsible for insuring proper dynamic and/or static extents, MemorySpace, Layout, etc.
\begin{code}[keywords={View, float, LayoutRight, HostSpace, MemoryTraits, Unmanaged}]
View<float**, LayoutRight, HostSpace>
  v_unmanaged(raw_ptr, N0, N1);
\end{code}}
        \end{itemize}

\end{frame}

\begin{frame}[fragile]{Module 3: Summary}

	\textbf{Atomic operations}
        \begin{itemize}
                \item Atomic functions available on the host or the device (e.g. \texttt{Kokkos::atomic\_add})
                \item {Use \texttt{Atomic} memory trait for atomic accesses on Views
\begin{code}[keywords={View,int,MemoryTraits,Atomic}]
View<int*> v("v", N0);
View<int*, MemoryTraits<Atomic>> v_atomic = v;
\end{code}}
                \item Use \texttt{ScatterView} for scatter-add parallel pattern
        \end{itemize}

        \vspace{10pt}
	\textbf{Dual Views}
        \begin{itemize}
                \item For managing data synchronization between host and device
 		\item Helps in codes with no holistic view of data flow
		\begin{itemize}
                   \item In particular when porting codes incrementally
                \end{itemize}
        \end{itemize}

\end{frame}
\begin{frame}{Module 4: Hierarchical Parallelism (08/07)}

	\vspace{5pt}
	\textbf{Hierarchical Parallelism}
	\begin{itemize}
        \item How to leverage more parallelism through nested loops.
        \item The concept of Thread-Teams and Vectorlength.
	\end{itemize}

	\vspace{5pt}
	\textbf{Scratch Space}
	\begin{itemize}
        \item Getting temporary workspace in kernels.
        \item Leveraging GPU Shared Memory.
	\end{itemize}

        \vspace{5pt}
        \textbf{Unique Token}
        \begin{itemize}
        \item How to acquire safely per-thread resources.
        \end{itemize}

\end{frame}

\input{../sections/Section_Hierarchical}
\input{../sections/Section_ScratchSpace}
\input{../sections/Section_UniqueToken}

\begin{frame}[fragile]{Module 4: Summary}
	\textbf{Hierarchal Parallelism}
  \begin{itemize}
    \item{\textbf{Hierarchical work} can be parallelized via hierarchical parallelism.}
    \item{Hierarchical parallelism is leveraged using \textbf{thread teams} launched with a \texttt{TeamPolicy}.}
    \item{Team ``worksets'' are processed by a team in nested \texttt{parallel\_for} (or \texttt{reduce} or \texttt{scan}) calls with a \texttt{TeamThreadRange} and \texttt{ThreadVectorRange} policy.}
    \item{Execution can be restricted to a subset of the team with the \texttt{single} pattern using either a \texttt{PerTeam} or \texttt{PerThread} policy.}
    \item{Teams can be used to \textbf{reduce contention} for global resources even in ``flat'' algorithms.}
  \end{itemize}


  
\end{frame}

\begin{frame}[fragile]{Module 4: Summary}
   \textbf{Scratch Space}
\begin{itemize}
    \item{\textbf{Scratch Memory} can be use with the \texttt{TeamPolicy} to provide thread or team \textbf{private} memory.}
    \item{Usecase: per work-item temporary storage or manual caching.}
    \item{Scratch memory exposes on-chip user managed caches (e.g. on NVIDIA GPUs)}
    \item{The size must be determined before launching a kernel.}
    \item{Two levels are available: large/slow and small/fast.}
  \end{itemize}
  \textbf{Unique Token}
  \begin{itemize}
    \item{\textbf{UniqueToken} give a thread safe portable way to divide thread specific resources}
    \item{\textbf{UniqueToken} can be sized to restrict ids to a range.}
    \item{A \textbf{Global} UniqueToken is available.}
  \end{itemize}

\end{frame}

\begin{frame}{Module 5: Outlook (08/14)}
    \vspace{-3pt}
	\textbf{Task Parallelism:}
	\begin{itemize}
        \item {Basic interface for fine-grained tasking in Kokkos}
        \item {How to express dynamic dependency structures in Kokkos}
	\end{itemize}
	
	\vspace{5pt}
	\textbf{Streams: Concurrent Execution Spaces}
	\begin{itemize}
		\item {How to use Streams within Kokkos Execution spaces}
	\end{itemize}

	\vspace{5pt}
	\textbf{SIMD: Portable vector intrinsic types}
	\begin{itemize}
		\item {How to use SIMD types to improve vectorization}
		\item {Alternative to ThreadVector loops and outer loop vectorization}
	\end{itemize}

	\vspace{5pt}
    \textbf{Slack channel:} {\scriptsize \url{https://kokkosteam.slack.com/}}
	
	\vspace{5pt}
	\textbf{Recordings/Slides:} {\scriptsize \url{https://kokkos.org/kokkos-core-wiki/videolectures.html}}

\end{frame}

\end{document}

