
%==========================================================================

\begin{frame}[fragile]

  {\Huge Organizational}

  \vspace{15pt}

  \begin{itemize}
    \item Targeting C++20 for Kokkos 5.0
    \item Minimum Requirements for Kokkos 5.0
    \item Mailing Lists
  \end{itemize}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Kokkos 5 and ISO C++20}
\begin{center}
\textbf{Kokkos 5 is coming October-November 2025}

\vspace{0.5cm}
\textbf{This will require C++20!}
\end{center}

\textit{Start preparing now:}
\begin{itemize}
  \item{Check availability of compilers on your systems}
  \item{Test with C++20 enabled: start with a CPU build}
  \item{Minimum Compiler requirements will change}
\end{itemize}

\vspace{0.5cm}

Release 4.7 will be the last release before Kokkos 5.0, supported until July 2026

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Kokkos 5 minimum requirements}

\begin{table}[]
\begin{tabular}{lll}
\multicolumn{1}{r}{} & Kokkos 4.x & Kokkos 5.0 \\ \hline
GCC                  & 8.2.0      & 10.4.0     \\
Clang (CPU)          & 8.0.0      & 14.0.0     \\
Clang (CUDA)         & 10.0.0     & 14.0.0     \\
Clang (OpenMPTarget) & 15.0.0     & 15.0.0     \\
IntelLLVM (CPU)      & 2021.1.1   & 2022.0.0   \\
IntelLLVM (SYCL)     & 2023.0.0   & 2024.2.1   \\
NVCC                 & 11.0       & 12.2.0     \\
NVC++                & 22.3       & 22.3       \\
ROCM                 & 5.2.0      & 6.2.0      \\
MSVC                 & 19.29      & 19.30      \\
ARM/Clang            & 20.1       & 20.1       \\ \hline
\end{tabular}
\end{table}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Kokkos Mailing Lists}

\vspace{0.5cm}
\begin{center}
Sign up for the Kokkos mailing list to stay up-to-date with the latest Kokkos news.
\end{center}

\vspace{0.5cm}

\begin{center}
\url{https://kokkos.org/community/mailing-lists/}
\end{center}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Kokkos Trademark}

Kokkos is a Linux Foundation project with a trademark!

\textbf{Why trademark enforcement is important}
\begin{itemize}
\item{\textbf{Avoiding confusion}: Users will want to know what is part of Kokkos, with LF rules, versus a project by third parties.}
\item{\textbf{Legal Protection}: Preserving the Kokkos project as an Open Source community may require us to protect the project against commercial takeover.}
\item{\textbf{User Trust}: Allows us to build up the Kokkos brand as a sign of quality and maturity.}
\end{itemize}

\begin{center}
The Kokkos trademark does NOT prevent you from using the word "Kokkos" in your slides, papers and websites!
\end{center}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{Trademark Do's and Don'ts}

\textbf{Do's}

\begin{itemize}
\item{We want you to publish and advertise your project using Kokkos!}
\item{We want you to publish on ideas to improve Kokkos!}
\end{itemize}

\textbf{Don'ts}

\begin{itemize}
\item{Do not imply that your effort is part of the Kokkos project if it isn't.}
\begin{itemize}
\item{Project Names are critical: Foo for Kokkos (GOOD); Kokkos-Foo (BAD)}
\item{The Kokkos project uses names such as Kokkos-Kernels, Kokkos-FFT, Kokkos-Comm that imply sub efforts in the Kokkos project.}
\end{itemize}
\item{Do not imply that the Kokkos project endorsed your effort if it hasn't.}
\end{itemize}

\end{frame}

%==========================================================================

