
%==========================================================================

\begin{frame}[fragile]{}

  {\Huge CMake Build Language}

  \vspace{10pt}

  \textbf{Content:}
  \begin{itemize}
    \item {Using CMakes Language Extension Support}
    \item {CUDA for Windows}
  \end{itemize}

  \vspace{-20pt}

\end{frame}

%==========================================================================

\begin{frame}[fragile]{What is CMake Language Support}
   Every source file CMake compiles has a \textit{language}

   \begin{itemize}
     \item {Default == file extension (.cpp, .c, .f90, ...)}
     \item {But you can set it: \texttt{set\_source\_files\_properties(f.bar PROPERTIES LANGUAGE CXX)}}
   \end{itemize}

   \textbf{Why does this matter for Kokkos?}

   \vspace{10pt}
   CMake treats some language extensions that way, but not all:
   
   \begin{itemize}
     \item {CUDA $->$ CMake language \texttt{CUDA}}
     \item {HIP $->$ CMake language \texttt{HIP}}
     \item {OpenMP $->$ \textbf{Not} a CMake language.}
     \item {SYCL $->$ \textbf{Not} a CMake language.}
   \end{itemize}
\end{frame}

\begin{frame}[fragile]{Kokkos and CMake Language}

  \textbf{Pre 3.6 behavior}

  \begin{itemize}
    \item {All Kokkos containing files are C++ files (CXX)}
    \item {Kokkos's build system adds compiler flags to make files CUDA, HIP, OpenMP, or SYCL}
    \begin{itemize}
      \item {We add \texttt{-fopenmp, -x cu, ...}}
    \end{itemize}
    \item {We use \texttt{nvcc\_wrapper} to make CMake not choke on \texttt{nvcc}}
  \end{itemize}

  \textbf{Advantages:}
  \begin{itemize}
    \item {Flags can be obtained via depending on target, language \texttt{NOT}}
    \item {Support for HIP before CMake supported it}
    \item {No need for users to set the correct language for each file - \textit{Note:} the \textit{need} propagates, the setting doesn't ...}
  \end{itemize}

  \textbf{Drawbacks:}
  \begin{itemize}
    \item {Not fully using CMakes native CUDA and HIP support}
    \item {\texttt{nvcc\_wrapper} only works on Linux}
  \end{itemize}

	
\end{frame}


\begin{frame}[fragile]{Kokkos and CMake Language}

  \textbf{3.6 behavior}

  
  \begin{itemize}
    \item {Default: same as pre 3.6}
    \item {Set \texttt{-DKokkos\_ENABLE\_COMPILE\_AS\_CMAKE\_LANGUAGE=ON} to use CMake Language mode.}
    \item {Use \texttt{set\_source\_files\_properties} on each source file depending on Kokkos}
    \begin{itemize}
      \item{We export \texttt{Kokkos\_COMPILE\_LANGUAGE} to make that portable}
    \end{itemize}
  \end{itemize}

  \textbf{Pifalls:}
  \begin{itemize}
    \item {\texttt{CMAKE\_CXX\_FLAGS} unused by Kokkos files}
    \begin{itemize} 
      \item{\texttt{CMAKE\_CUDA\_FLAGS} for CUDA (equiv. for HIP)}
      \item{\texttt{CMAKE\_CXX\_FLAGS} for SYCL/OpenMP etc.}
    \end{itemize}
    \item{YOU need to set \texttt{CMAKE\_CUDA\_ARCHITECTURES} downstream}
    \item{YOU need to add \texttt{Kokkos\_COMPILE\_LANGUAGE} to your project!}
    \item{For libraries: your users need to set all this too ..}
    \item{Interaction with MPI Wrappers iffy ...}
  \end{itemize}


\end{frame}

\begin{frame}[fragile]{CMake Language Example}
\textbf{Configure Kokkos:}
\begin{lstlisting}[language=bash]
cmake -DKokkos_ENABLE_CUDA=ON -DKokkos_ARCH_VOLTA70=ON \
  -DKokkos_ENABLE_COMPILE_AS_CMAKE_LANGUAGE=ON ${KOKKOS_SOURCE}
\end{lstlisting}

\textbf{Project CMakeLists.txt:}
\begin{lstlisting}[language=bash]
#find Kokkos before project declaration
find_package(Kokkos COMPONENTS separable_compilation)

project(Example CXX Fortran ${Kokkos_COMPILE_LANGUAGE})

set_source_files_properties(cmake_example.cpp PROPERTIES 
  LANGUAGE \${Kokkos_COMPILER_LANGUAGE})

add_executable(example cmake_example.cpp bar.cpp foo.f)

target_link_libraries(example Kokkos::kokkos)
\end{lstlisting}

\textbf{Configure Project:}

\begin{lstlisting}[language=bash]
cmake -DCMAKE_CUDA_ARCHITECTURES=70 ${PROJECT_SOURCE}
\end{lstlisting}

\end{frame}

\begin{frame}[fragile]{When Should One Use This?}
\textbf{Why should I use this, with all the complication?}
\begin{itemize}
  \item{You may want to use native CMake CUDA/HIP support}
  \item{You may hate \texttt{nvcc\_wrapper}}
  \item{But most importantly:}
\end{itemize}

\begin{center}
\textbf{This works in Visual Studio for MSVC + NVCC!}
\end{center}

\end{frame}
%==========================================================================
%
