
%==========================================================================

\begin{frame}[fragile]

  {\Huge Backend Updates}

  \vspace{10pt}

  \textbf{Content:}
  \begin{itemize}
    \item Backend Updates CUDA
    \item Backend Updates HIP
    \item Backend Updates SYCL
    \item Backend Updates OpenMPTarget
    \item Backend Updates OpenACC
  \end{itemize}

\end{frame}

%==========================================================================

\begin{frame}{Backend Updates CUDA}
\textbf{Miscellaneous}
\begin{itemize}
\item Link against CUDA libraries even with KOKKOS\_ENABLE\_COMPILE\_AS\_CMAKE\_LANGUAGE
\item Don't use the compiler launcher script if the compile language is CUDA.
\item nvcc(wrapper): adding "long" and "short" versions for all flags
\end{itemize}

\textbf{Multi-GPU Support from single process}
\begin{itemize}
\item Highly Experimental! (But most things should work now)
\item For now: via interoperability interfaces - i.e. no native interface to create execution space instances on different GPU
\item If you have interest: try it out and provide feedback
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Backend Updates CUDA}
\texttt{CUDA - multi-GPU support}
\begin{code}
  cudaStream_t[2] streams;
  cudaSetDevice(0);
  cudaStreamCreate(&streams[0]));
  cudaSetDevice(1);
  cudaStreamCreate(&streams[1]));
  {
    Kokkos::Cuda exec0(streams[0]), exec1[streams[1]);

    Kokkos::View<int *, TEST_EXECSPACE> view(Kokkos::view_alloc("v0", exec0), n);
    Kokkos::View<int *, TEST_EXECSPACE> view(Kokkos::view_alloc("v1", exec1), m);

    // run concurrently
    Kokkos::parallel_for(Kokkos::RangePolicy<Cuda>(exec0, 0, n), functor);
    Kokkos::parallel_for(Kokkos::RangePolicy<Cuda>(exec1, 0, m), functor);
  }
  cudaStreamDestroy(streams[0]);
  cudaStreamDestroy(streams[1]);
\end{code}
\end{frame}


\begin{frame}[fragile]{Backend Updates HIP}
\begin{itemize}
\item Fix compilation error with amdclang++ 5.7 and newer when
  relocatable device code is enabled. We are aware of issues with older
  versions of amdclang++ when relocatable device code is enabled.
\item Added support for rocThrust (used in sort). Note that some
  installation of ROCm do not have rocThrust installed. rocThrust support
  can be enable/disabled using kokkos\_ENABLE\_ROCTHRUST
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Backend Updates SYCL}
\begin{itemize}
\item Only allow ext\_oneapi\_*-type devices when targeting GPUs
\item Avoid unnecessary zero-memset of the scratch flags in SYCL
\item Use host-pinned memory to copy reduction/scan result
\item Address deprecations after oneAPI 2023.2.0 
\item Make sure to call find\_dependency for oneDPL if necessary
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Backend Updates OpenMPTarget}
\begin{itemize}
\item Intel GPUs - Allow printing from GPUs.
\item NVIDIA and AMD GPUs - LLVM extensions for dynamic shared memory
\begin{itemize}
    \item Available since LLVM/18
    \item Only available in upstream LLVM 
    \item Not part of OpenMP API
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Backend Updates OpenACC}
\begin{itemize}
\item Add support for atomic operations
\begin{itemize}
    \item OpenACC does not support atomic-compare-exchange operations; implemented using CUDA intrinics (atomicCAS).
    \item Can be compiled by NVIDIA NVHPC compiler (nvc++) but not by CLACC compiler.
    \item Support only NVIDIA GPUs.
\end{itemize}
\item Change the default execution policy behavior from synchronous to asynchronous executions.
\end{itemize}
\end{frame}


%==========================================================================

